STAT 133 Final Project: Visualizing Berkeley Police Data

### 2016-08-09 final_paper/finalpaper.Rmd
figures

```{r, echo=FALSE, warning=F,message=F, fig.align="center", fig.width = 20, fig.height=15}
map_arrested1 
```

```{r, echo=FALSE, warning = FALSE, message=FALSE, fig.cap= "Police Stops Leading to Arrests", fig.align = "center", fig.width = 8, fig.height = 3}
map_enforcement
```

>>>>

```{r, echo=FALSE, warning=F,message=F, fig.cap= "Police Stops Leading to Arrests", fig.align="center", fig.width = 10, fig.height=5}
map_arrested1 
```

```{r, echo=FALSE, warning = FALSE, message=FALSE, fig.align = "center", fig.width = 5, fig.height = 3}
map_enforcement
```
